About this blog

### 2021-11-23 _post/2021-07-18-the-ibizia-inquiry-in-numbers/the-ibizia-inquiry-in-numbers.Rmd
updating with latest changes

author:  
  - first_name: "Roland"
    last_name: "Schmidt"
    url: https://werk.statt.codes
    orcid_id: 0000-0002-6897-1693
categories:
  - Austria
  - Parliament
  - web scraping
preview: the-ibizia-inquiry-in-numbers_files/images/subpage_link_to_transcript.PNG
output:
  distill::distill_article:
    toc: true
    toc_depth: 3
    toc_float: true
    self_contained: false
    code_folding: TRUE
draft: FALSE
creative_commons: CC BY-NC-SA
editor_options: 
  chunk_output_type: console
---

@@

If you are not interested in any of the coding steps generating the data, jump directly to the [Analysis] section which still contains plenty of code, but you're not burdened with how to obtain the data in the first place.

>>>>

author:  
  - first_name: "Roland"
    last_name: "Schmidt"
    url: https://werk.statt.codes
    orcid_id: 0000-0002-6897-1693
categories:
  - Austria
  - Parliament
  - web scraping
preview: the-ibizia-inquiry-in-numbers_files/images/amused_graph.png
output:
  distill::distill_article:
    toc: true
    toc_depth: 3
    toc_float: true
    self_contained: false
    code_folding: TRUE
draft: FALSE
creative_commons: CC BY-NC-SA
editor_options: 
  chunk_output_type: console
---

@@

*If you are not interested in any of the coding steps generating the data, jump directly to the [Analysis] section* which still contains plenty of code, but you're not burdened with how to obtain the data in the first place.

### 2021-11-23 about.Rmd
main update
updating with latest changes

@@

Codes are collected at [www.github.com/werkstattcodes](https://github.com/werkstattcodes){target="_blank"}
Tweets are at @zoowalk.

>>>>

Note that I recently moved this blog and hence a few entries are somewhat 'messy' (broken links, images out of place). I'll hope to be able to iron this out soon.

@@

Codes are collected at [www.github.com/werkstattcodes](https://github.com/werkstattcodes){target="_blank"}.
Tweets are at [`@zoowalk`](https://twitter.com/zoowalk){target="_blank"}.
